MG7: Configurable and scalable 16S data analysis

### 2016-07-25 docs/mg7-paper/out/paper.tex
switch to initials in credits

\protect\hyperlink{statika}{Statika} is a Scala library developed by the
first and last authors which serves as a way of defining and composing
machine behaviors statically. The main component are \textbf{bundles}.
Each bundle declares a sequence of computations (its behavior) which
will be executed in an \textbf{environment}. A bundle can \emph{depend}
on other bundles, and when being executed by an environment, its DAG
(Directed Acyclic Graph) of dependencies is linearized and run in
sequence. In our use, bundles correspond to what an EC2 instance should
do and an environment to an AMI (Amazon Machine Image) which prepares
the basic configuration, downloads the Scala code and runs it.

@@

\protect\hyperlink{datasets}{Datasets} is a Scala library developed by
the first and last authors with the goal of being a Scala-embedded
mini-language for datasets and their locations. \textbf{Data} is
represented as type-indexed fields: keys are modeled as singleton types,
and values correspond to what could be called a denotation of the key: a
value of type \texttt{Location} tagged with the key type. Then a
\textbf{Dataset} is essentially a collection of data, which are
guaranteed statically to be different through type-level predicates,
making use of the value--type correspondence which can be established
through singleton types and implicits. A dataset location is then just a
list of locations formed by locations of each dataset key. All this is
based on what could be described as an embedding in Scala of an
extensible record system with concatenation on disjoint labels, in the
spirit of \citep{harper1990extensible} \citep{harper1991record}. For
that \emph{Datasets} uses the {[}ohnosequences/cosas{]}{[}cosas{]}
library.

@@

\protect\hyperlink{loquat}{Loquat} is a library developed by the first,
second and last authors designed for the execution of embarrassingly
parallel tasks using S3, SQS and EC2 Amazon services.

>>>>

\protect\hyperlink{statika}{Statika} is a Scala library developed by
\emph{AA} and \emph{EP-T} which serves as a way of defining and
composing machine behaviors statically. The main component are
\textbf{bundles}. Each bundle declares a sequence of computations (its
behavior) which will be executed in an \textbf{environment}. A bundle
can \emph{depend} on other bundles, and when being executed by an
environment, its DAG (Directed Acyclic Graph) of dependencies is
linearized and run in sequence. In our use, bundles correspond to what
an EC2 instance should do and an environment to an AMI (Amazon Machine
Image) which prepares the basic configuration, downloads the Scala code
and runs it.

@@

\protect\hyperlink{datasets}{Datasets} is a Scala library developed by
\emph{AA} and \emph{EP-T} with the goal of being a Scala-embedded
mini-language for datasets and their locations. \textbf{Data} is
represented as type-indexed fields: keys are modeled as singleton types,
and values correspond to what could be called a denotation of the key: a
value of type \texttt{Location} tagged with the key type. Then a
\textbf{Dataset} is essentially a collection of data, which are
guaranteed statically to be different through type-level predicates,
making use of the value--type correspondence which can be established
through singleton types and implicits. A dataset location is then just a
list of locations formed by locations of each dataset key. All this is
based on what could be described as an embedding in Scala of an
extensible record system with concatenation on disjoint labels, in the
spirit of \citep{harper1990extensible} \citep{harper1991record}. For
that \emph{Datasets} uses the {[}ohnosequences/cosas{]}{[}cosas{]}
library.

@@

\protect\hyperlink{loquat}{Loquat} is a library developed by \emph{AA},
\emph{EK} and \emph{EP-T} designed for the execution of embarrassingly
parallel tasks using S3, SQS and EC2 Amazon services.
